Halo alignments with large scale tidal and velocity fields

### 2013-04-08 paper/main.tex
more text on other people's results

@@

The simulation is the millennium simulation, which has $2160^3$
particles in a volume of $500$\hMpc on a side. This corresponds to a
particle mass of $8.6\times 10^{8}$\hMsun. The catalog uses both halos
and subhalos which were identified with SUBFIND. Only halos with more
than 500 particles were kept to get a robust computation for the spin.

However the analysis are reported ona box of $300$\hMpc on a
side. Four different gaussian smoothing scales are used:

The method to define the filamentary structure is based on the
eigenvalues of the hessian of the density.

>>>>

\begin{table}
\begin{tabular}{llll}
Author & Web Method & Halo Finder & SPIN \\
\end{tabular}
SPIN
\end{table}

@@

The simulation is the millennium simulation, which has $2160^3$
particles in a volume of $500$\hMpc on a side. This corresponds to a
particle mass of $8.6\times 10^{8}$\hMsun. The catalog uses both halos
and subhalos which were identified with SUBFIND. Only halos with more
than 500 particles were kept to get a robust computation for the
spin. For each halo the spin is defined as the sum of the angular momentum
of each particle with respect to the center of mass.

The method to define the filamentary structure is based on the
eigenvalues of the hessian of the density.However the analysis are
reported ona box of $300$\hMpc on a side. Four different gaussian
smoothing scales are used: $2.0$, $3.0$ and $5.0$\hMpc.

The authors report a slight alignment signal of spin against the
principal filament axis. By fitting the following functional form to
the $\cos(\theta)$ distribution

\begin{equation}
P(\cos\theta) =
(1-c)\sqrt{1+\frac{c}{2}}\left[1-c\left(1-\frac{3}{2}\cos^{2}\theta \right)\right]^{-3/2},
\end{equation}

they are able to quantify the degree of alignment ($c<0$) or
antialignment ($c>0$).  This parameterization is based on theoretical
expectactions of Tidal Torque Theory (TTT) \citep{Lee2005}. At $z=0$, the reported
value is $c = −0.035 \pm 0.004$, where the uncertainty was calculated
using bootstraping and resampling.

When the halo sample is divided between low mass and high mass halos
with a transition scale $M_{\star}=5.9\times 10^{12}$\Msun, there is
an anti-alignment above this mass and an alignment below it.
